---
title: "saadams_OriginalHomeworkCode_02"
format: html
editor: visual
---

# Homework 2: Titis in the Mist

## The Scenario
Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## Question 1
What is the probability that she will hear more than 8 calls during any given session?

```{r}
1 - ppois(q = 7, lambda = 15) # P(x>=8) = 1 - probability(x<8)
```

## Question 2
What is the probability that she will hear no calls in a session?
```{r}
dpois(x = 0, lambda = 15)
```

## Question 3
What is the probability that she will hear exactly 3 calls in a session?

## Question 4
Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

## Question 5
Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

## Question 6
Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?



